---
title: "geographic_cpoints_inversions"
author: "Arne Jacobs"
date: "11/10/2020"
output: github_document
highlight: pygments
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
names(knitr::knit_engines$get())
```

Load R-packages:
```{r, eval=F, include=F}
#Plotting:
library(tidyverse)
library(ggfortify)
library(RColorBrewer)
library(wesanderson)
library(cowplot)
library(ggridges)
library(reshape2)
library(ggtree)
library(patchwork)
library(lmerTest)
library(lme4)
library(scales)
library(windowscanr)
library(corrr)
library(vegan)
library(conStruct)
library(ade4)
library(gradientForest)
library(matrixcalc)
library(report)

```



# Estimating inversion frequencies from PCA 


## Results for all populations

PCA based on covariance matrix from one-read sampling in angsd

```{r, eval = FALSE}
cov.inv24.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv24_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv24.m.pca=eigen(cov.inv24.m)
x <- sum(cov.inv24.m.pca$values)
varPC1 <- (cov.inv24.m.pca$values[1]/x)*100
varPC2 <- (cov.inv24.m.pca$values[2]/x)*100

cov.inv24.m.pca=as_tibble(cov.inv24.m.pca$vectors)
names(cov.inv24.m.pca)[1]=c("PC1")
names(cov.inv24.m.pca)[2]=c("PC2")
cov.inv24.m.pca.df=as_tibble(cbind(ind.df, cov.inv24.m.pca))
cov.inv24.m.pca.df$Pop <- ordered(cov.inv24.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))
x <- sum(cov.inv24.m.pca$values)
varPC1 <- (cov.inv24.m.pca$values[1]/x)*100
varPC2 <- (cov.inv24.m.pca$values[2]/x)*100
mme.pal <- c("#4f000b","#9e2a2b","#CE4257","darkorange2", "#ff9b54","#FFC100", "#edd746","#2a9d8f","#0f85a0","#05668D","#98C1d9", "#3d5a80") 

inv24.pca = ggplot(data=cov.inv24.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal)


ggplot(data=cov.inv24.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv24.m.pca.df.filt=filter(cov.inv24.m.pca.df, Ind != "JIGA_1070")
cov.inv24.m.pca.df.filt=cov.inv24.m.pca.df.filt[,1:4]
cov.inv24.m.pca.df.filt$SAllele = if_else(condition = cov.inv24.m.pca.df.filt$PC1 < -0.05, "S", "Other")
cov.inv24.m.pca.df.filt$NAllele = if_else(condition = cov.inv24.m.pca.df.filt$PC1 > 0, "N", "Other")
cov.inv24.m.pca.df.filt$HET = if_else(condition = cov.inv24.m.pca.df.filt$SAllele == cov.inv24.m.pca.df.filt$NAllele, "HET", "NA")


#karyotypes:
cov.inv24.m.pca.df.filt.HET = filter(cov.inv24.m.pca.df.filt, HET == "HET")
cov.inv24.m.pca.df.filt.HET$ktype = "het"

cov.inv24.m.pca.df.filt.S = filter(cov.inv24.m.pca.df.filt, SAllele == "S")
cov.inv24.m.pca.df.filt.S$ktype = "south"

cov.inv24.m.pca.df.filt.N = filter(cov.inv24.m.pca.df.filt, NAllele == "N")
cov.inv24.m.pca.df.filt.N$ktype = "north"

inv24.pca.karyotypes.df = as_tibble(rbind(cov.inv24.m.pca.df.filt.S[,c(1,2,3,4,8)],
                                cov.inv24.m.pca.df.filt.N[,c(1,2,3,4,8)],
                                cov.inv24.m.pca.df.filt.HET[,c(1,2,3,4,8)]))
write_csv(inv24.pca.karyotypes.df,"~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/Inv24_ind_karyotypes_allpops.csv")


#Population frequencies
pop = as.vector(unique(cov.inv24.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv24.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr24.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr24.df) = c("Prop.S.Allele.chr24","Pop")
```


```{r, eval = FALSE}
cov.inv19.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv19_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv19.m.pca=eigen(cov.inv19.m)
cov.inv19.m.pca=as_tibble(cov.inv19.m.pca$vectors)
names(cov.inv19.m.pca)[1]=c("PC1")
names(cov.inv19.m.pca)[2]=c("PC2")
cov.inv19.m.pca.df=as_tibble(cbind(ind.df, cov.inv19.m.pca))
cov.inv19.m.pca.df$Pop <- ordered(cov.inv19.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv19.pca = ggplot(data=cov.inv19.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal) +
  theme(legend.position = "NA")

ggplot(data=cov.inv19.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv19.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv19.m.pca.df.filt=filter(cov.inv19.m.pca.df, Ind != "JIGA_1070")
cov.inv19.m.pca.df.filt=cov.inv19.m.pca.df.filt[,1:4]
cov.inv19.m.pca.df.filt$SAllele = if_else(condition = cov.inv19.m.pca.df.filt$PC1 < -0.05, "S", "Other")
cov.inv19.m.pca.df.filt$NAllele = if_else(condition = cov.inv19.m.pca.df.filt$PC1 > 0, "N", "Other")

pop = as.vector(unique(cov.inv19.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv19.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr19.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr19.df) = c("Prop.S.Allele.chr19","Pop")
```

```{r, eval = FALSE}
cov.inv18.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv18_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv18.m.pca=eigen(cov.inv18.m)
cov.inv18.m.pca=as_tibble(cov.inv18.m.pca$vectors)
names(cov.inv18.m.pca)[1]=c("PC1")
names(cov.inv18.m.pca)[2]=c("PC2")
cov.inv18.m.pca.df=as_tibble(cbind(ind.df, cov.inv18.m.pca))
cov.inv18.m.pca.df$Pop <- ordered(cov.inv18.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv18.pca = ggplot(data=cov.inv18.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal) +
  theme(legend.position = "NA")

ggplot(data=cov.inv18.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv18.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv18.m.pca.df.filt=filter(cov.inv18.m.pca.df, Ind != "JIGA_1070")
cov.inv18.m.pca.df.filt=cov.inv18.m.pca.df.filt[,1:4]
cov.inv18.m.pca.df.filt$SAllele = if_else(condition = cov.inv18.m.pca.df.filt$PC1 > 0.06, "S", "Other")
cov.inv18.m.pca.df.filt$NAllele = if_else(condition = cov.inv18.m.pca.df.filt$PC1 < 0, "N", "Other")
cov.inv18.m.pca.df.filt$HET = if_else(condition = cov.inv18.m.pca.df.filt$SAllele == cov.inv18.m.pca.df.filt$NAllele, "HET", "NA")


#karyotypes:
cov.inv18.m.pca.df.filt.HET = filter(cov.inv18.m.pca.df.filt, HET == "HET")
cov.inv18.m.pca.df.filt.HET$ktype = "het"

cov.inv18.m.pca.df.filt.S = filter(cov.inv18.m.pca.df.filt, SAllele == "S")
cov.inv18.m.pca.df.filt.S$ktype = "south"

cov.inv18.m.pca.df.filt.N = filter(cov.inv18.m.pca.df.filt, NAllele == "N")
cov.inv18.m.pca.df.filt.N$ktype = "north"

inv18.pca.karyotypes.df = as_tibble(rbind(cov.inv18.m.pca.df.filt.S[,c(1,2,3,4,8)],
                                cov.inv18.m.pca.df.filt.N[,c(1,2,3,4,8)],
                                cov.inv18.m.pca.df.filt.HET[,c(1,2,3,4,8)]))
write_csv(inv18.pca.karyotypes.df,"~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/Inv18_ind_karyotypes_allpops.csv")

pop = as.vector(unique(cov.inv18.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv18.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr18.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr18.df) = c("Prop.S.Allele.chr18","Pop")
```


Estimate for chr11
```{r, eval = FALSE}
cov.inv11.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv11_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage//Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv11.m.pca=eigen(cov.inv11.m)
cov.inv11.m.pca=as_tibble(cov.inv11.m.pca$vectors)
names(cov.inv11.m.pca)[1]=c("PC1")
names(cov.inv11.m.pca)[2]=c("PC2")
cov.inv11.m.pca.df=as_tibble(cbind(ind.df, cov.inv11.m.pca))
cov.inv11.m.pca.df$Pop <- ordered(cov.inv11.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv11.pca = ggplot(data=cov.inv11.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal) +
  theme(legend.position = "NA")

ggplot(data=cov.inv11.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv11.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv11.m.pca.df.filt=filter(cov.inv11.m.pca.df, Ind != "JIGA_1070")
cov.inv11.m.pca.df.filt=cov.inv11.m.pca.df.filt[,1:4]
cov.inv11.m.pca.df.filt$SAllele = if_else(condition = cov.inv11.m.pca.df.filt$PC1 < -0.025, "S", "Other")
cov.inv11.m.pca.df.filt$NAllele = if_else(condition = cov.inv11.m.pca.df.filt$PC1 > 0.05, "N", "Other")
cov.inv11.m.pca.df.filt$HET = if_else(condition = cov.inv11.m.pca.df.filt$SAllele == cov.inv11.m.pca.df.filt$NAllele, "HET", "NA")


#karyotypes:
cov.inv11.m.pca.df.filt.HET = filter(cov.inv11.m.pca.df.filt, HET == "HET")
cov.inv11.m.pca.df.filt.HET$ktype = "het"

cov.inv11.m.pca.df.filt.S = filter(cov.inv11.m.pca.df.filt, SAllele == "S")
cov.inv11.m.pca.df.filt.S$ktype = "south"

cov.inv11.m.pca.df.filt.N = filter(cov.inv11.m.pca.df.filt, NAllele == "N")
cov.inv11.m.pca.df.filt.N$ktype = "north"

inv11.pca.karyotypes.df = as_tibble(rbind(cov.inv11.m.pca.df.filt.S[,c(1,2,3,4,8)],
                                cov.inv11.m.pca.df.filt.N[,c(1,2,3,4,8)],
                                cov.inv11.m.pca.df.filt.HET[,c(1,2,3,4,8)]))
write_csv(inv11.pca.karyotypes.df,"~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/Inv11_ind_karyotypes_allpops.csv")

pop = as.vector(unique(cov.inv11.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv11.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr11.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr11.df) = c("Prop.S.Allele.chr11","Pop")
```

```{r, eval = FALSE}
cov.inv8.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv8_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv8.m.pca=eigen(cov.inv8.m)
cov.inv8.m.pca=as_tibble(cov.inv8.m.pca$vectors)
names(cov.inv8.m.pca)[1]=c("PC1")
names(cov.inv8.m.pca)[2]=c("PC2")
cov.inv8.m.pca.df=as_tibble(cbind(ind.df, cov.inv8.m.pca))
cov.inv8.m.pca.df$Pop <- ordered(cov.inv8.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv8.pca = ggplot(data=cov.inv8.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal)+
  theme(legend.position = "NA")

ggplot(data=cov.inv8.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv8.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv8.m.pca.df.filt=filter(cov.inv8.m.pca.df, Ind != "JIGA_1070", Ind != "MDME42")
cov.inv8.m.pca.df.filt=cov.inv8.m.pca.df.filt[,1:4]
cov.inv8.m.pca.df.filt$SAllele = if_else(condition = cov.inv8.m.pca.df.filt$PC1 > 0.075, "S", "Other")
cov.inv8.m.pca.df.filt$NAllele = if_else(condition = cov.inv8.m.pca.df.filt$PC1 < 0.02, "N", "Other")

pop = as.vector(unique(cov.inv8.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv8.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr8.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr8.df) = c("Prop.S.Allele.chr8","Pop")
```

```{r, eval = FALSE}
cov.inv7.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv7_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv7.m.pca=eigen(cov.inv7.m)
cov.inv7.m.pca=as_tibble(cov.inv7.m.pca$vectors)
names(cov.inv7.m.pca)[1]=c("PC1")
names(cov.inv7.m.pca)[2]=c("PC2")
cov.inv7.m.pca.df=as_tibble(cbind(ind.df, cov.inv7.m.pca))
cov.inv7.m.pca.df$Pop <- ordered(cov.inv7.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv7.pca = ggplot(data=cov.inv7.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal)+
  theme(legend.position = "NA")

ggplot(data=cov.inv7.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv7.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv7.m.pca.df.filt=filter(cov.inv7.m.pca.df, Ind != "JIGA_1070")
cov.inv7.m.pca.df.filt=cov.inv7.m.pca.df.filt[,1:4]
cov.inv7.m.pca.df.filt$SAllele = if_else(condition = cov.inv7.m.pca.df.filt$PC1 > 0.05, "S", "Other")
cov.inv7.m.pca.df.filt$NAllele = if_else(condition = cov.inv7.m.pca.df.filt$PC1 < 0, "N", "Other")

pop = as.vector(unique(cov.inv7.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv7.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr7.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr7.df) = c("Prop.S.Allele.chr7","Pop")
```

```{r, eval = FALSE}
cov.inv4.m=as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_inv4_filtsnps_ibs.covMat"))
ind.df=read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
cov.inv4.m.pca=eigen(cov.inv4.m)
cov.inv4.m.pca=as_tibble(cov.inv4.m.pca$vectors)
names(cov.inv4.m.pca)[1]=c("PC1")
names(cov.inv4.m.pca)[2]=c("PC2")
cov.inv4.m.pca.df=as_tibble(cbind(ind.df, cov.inv4.m.pca))
cov.inv4.m.pca.df$Pop <- ordered(cov.inv4.m.pca.df$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS", "HXNS", "MAQU"))

inv4.pca = ggplot(data=cov.inv4.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21) +
  scale_fill_manual(values = mme.pal) +
  scale_colour_manual(values = mme.pal) +
  theme(legend.position = "NA")

ggplot(data=cov.inv4.m.pca.df, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=cov.inv4.m.pca.df, aes(x=PC1,y=Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
cov.inv4.m.pca.df.filt=filter(cov.inv4.m.pca.df, Ind != "JIGA_1070", Ind != "MCCT_M24", Ind != "MCCT_M04", Ind != "MCCT_M18", Ind != "OINC19")
cov.inv4.m.pca.df.filt=cov.inv4.m.pca.df.filt[,1:4]
cov.inv4.m.pca.df.filt$SAllele = if_else(condition = cov.inv4.m.pca.df.filt$PC1 > 0.0375, "S", "Other")
cov.inv4.m.pca.df.filt$NAllele = if_else(condition = cov.inv4.m.pca.df.filt$PC1 < 0, "N", "Other")

pop = as.vector(unique(cov.inv4.m.pca.df.filt$Pop))
Prop.S.Allele2 <- list()
for (i in pop) { 
  df = filter(cov.inv4.m.pca.df.filt, Pop == i)
  Sallele.pure = length((filter(df, SAllele == "S"))$Ind)*2 
  Nallele.pure  = length((filter(df, NAllele == "N"))$Ind)*2 
  HETind = ((length(df$Ind)) - (Sallele.pure/2 + Nallele.pure/2))
  Sallele = Sallele.pure + HETind/2
  Nallele = Nallele.pure + HETind/2
  Alleles = length(df$Ind)*2
  Prop.S.Allele = Sallele/Alleles
  Prop.S.Allele2[[i]] <- Prop.S.Allele
}

Prop.S.Allele.chr4.df = as_tibble(cbind(as.data.frame(rbind(Prop.S.Allele2$JIGA, Prop.S.Allele2$LRSC, Prop.S.Allele2$MCNC, Prop.S.Allele2$OINC, Prop.S.Allele2$CTVA, Prop.S.Allele2$PANY, Prop.S.Allele2$MCCT, Prop.S.Allele2$DXMA, Prop.S.Allele2$MDME, Prop.S.Allele2$MBNS, Prop.S.Allele2$HXNS, Prop.S.Allele2$MAQU))$V1, c("JIGA","LRSC","MCNC","OINC","CTVA","PANY","MCCT","DXMA","MDME","MBNS","HXNS","MAQU")))
names(Prop.S.Allele.chr4.df) = c("Prop.S.Allele.chr4","Pop")
```

Combine PCA plots
```{r, eval = FALSE}
inv.pca = (inv4.pca | inv7.pca | inv8.pca | inv19.pca) / (inv11.pca | inv18.pca | inv24.pca) 

inv.pca + plot_annotation(tag_levels = 'A')
```




Combine all dataframes and plot inversion frequency cpoints
```{r, eval = FALSE}
Prop.S.Alleles.df = as_tibble(as.data.frame(cbind(Prop.S.Allele.chr4.df,Prop.S.Allele.chr7.df,
                                    Prop.S.Allele.chr8.df,Prop.S.Allele.chr11.df,Prop.S.Allele.chr18.df,
                                    Prop.S.Allele.chr19.df,Prop.S.Allele.chr24.1.df,
                                    Prop.S.Allele.chr24.df))[,c(2,1,3,5,7,9,11,13,15)])

#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)

inv4 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr4)) +
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr4), method = "loess")
inv7 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr7))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr7), method = "loess")
inv8 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr8))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr8), method = "loess")
inv11 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr11))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr11), method = "loess")
inv18 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr18))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr18), method = "loess")
inv19 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr19))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr19), method = "loess")
inv24.1 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr24.1))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr24.1), method = "loess")
inv24 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr24))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr24), method = "loess")

inv.cpoints = (inv4 | inv7 | inv8| inv11) / (inv18 | inv19 | inv24.1 | inv24)

inv4 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr4)) +
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr4), method = "loess")
inv7 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr7))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr7), method = "loess")
inv8 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr8))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr8), method = "loess")
inv11 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr11))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr11), method = "loess")
inv18 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr18))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr18), method = "loess")
inv19 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr19))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr19), method = "loess")
inv24.1 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr24.1))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr24.1), method = "loess")
inv24 = ggplot(data = Prop.S.Alleles.df2) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr24))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr24), method = "loess")

inv.cpoint.dist = (inv4 | inv7 | inv8 | inv11) / (inv18 | inv19 | inv24.1 | inv24)
```


## Plot inversion and neutral clines without HXNS and MAQU

Combine all dataframes and plot inversion frequency cpoints
```{r, eval = FALSE}
Prop.S.Alleles.df = as_tibble(as.data.frame(cbind(Prop.S.Allele.chr4.df,Prop.S.Allele.chr7.df,
                                    Prop.S.Allele.chr8.df,Prop.S.Allele.chr11.df,Prop.S.Allele.chr18.df,
                                    Prop.S.Allele.chr19.df,Prop.S.Allele.chr24.1.df,
                                    Prop.S.Allele.chr24.df))[,c(2,1,3,5,7,9,11,13,15)])

write_csv(Prop.S.Alleles.df, "~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_phenotype_associatons/InvFreq_southernAllele_allpops.csv")

#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)

Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")


inv4 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr4)) +
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr4), method = "loess")
inv7 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr7))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr7), method = "loess")
inv8 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr8))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr8), method = "loess")
inv11 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr11))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr11), method = "loess")
inv18 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr18))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr18), method = "loess")
inv19 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr19))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr19), method = "loess")
inv24 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=lat, y=Prop.S.Allele.chr24))+
  geom_smooth(aes(x=lat, y=Prop.S.Allele.chr24), method = "loess")

inv.cpoints = (inv4 | inv7 | inv8| inv11) / (inv18 | inv19 | inv24)

inv4 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr4)) +
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr4), method = "loess")
inv7 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr7))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr7), method = "loess")
inv8 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr8))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr8), method = "loess")
inv11 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr11))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr11), method = "loess")
inv18 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr18))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr18), method = "loess")
inv19 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr19))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr19), method = "loess")
inv24 = ggplot(data = Prop.S.Alleles.df2.filt) +
  geom_point(aes(x=Dist, y=Prop.S.Allele.chr24))+
  geom_smooth(aes(x=Dist, y=Prop.S.Allele.chr24), method = "loess")

inv.cpoint.dist = (inv4 | inv7 | inv8 | inv11) / (inv18 | inv19 | inv24)
```


```{r, eval = FALSE}
Mme.cov.thinned.noinv <- as.matrix(read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/pca_admix_mme_thinnedsnps_noinv.cov", header = F))
Ind.id <- read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
mme.pca <- eigen(Mme.cov.thinned.noinv)
eigenvectors <- (mme.pca$vectors)
pca.vectors <- cbind(Ind.id, eigenvectors)
names(pca.vectors)[3] <- "PC1"
names(pca.vectors)[4] <- "PC2"
pca.vectors.filt = filter(pca.vectors, Pop != "HXNS", Pop != "MAQU")
pca.vectors.filt$Pop <- ordered(pca.vectors.filt$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS"))

ggplot(data=pca.vectors.filt, aes(x=PC1,y=PC2, colour = Pop)) +
  geom_point(size = 4, shape=21)

ggplot(data=pca.vectors.filt, aes(x=PC1,y=Pop, colour = Pop)) +
  geom_point(size = 4, shape=21)

#Estimate the frequency of the southern allele by population
#Remove individual JIGA_1070 as it shows a weird pattern (intermediate between S-Allele and HET)
pca.vectors.df.filt=as_tibble(pca.vectors.filt)
pca.vectors.df.filt=pca.vectors.df.filt[,1:3]

ggplot(data=pca.vectors.df.filt, aes(x=-PC1,y=Pop, colour = Pop)) +
  geom_point(size = 4, shape=21)

#Add latitude from population information dataframe
pop <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
pop.filt = filter(pop, Pop != "HXNS", Pop != "MAQU")
pca.vectors.df.filt2 = left_join(pca.vectors.df.filt, pop.filt, by="Pop")
#Add distance from JIGA to dataframe
dist <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
pca.vectors.df.filt2 = left_join(pca.vectors.df.filt2, dist, by="Pop")

anc = ggplot(data = pca.vectors.df.filt2) +
  geom_point(aes(x=Dist, y=-PC1, colour = Pop)) +
  geom_smooth(aes(x=Dist, y=-PC1), method = "loess", span = 0.5)
anc
```


Plot neutral admixture proportions for K=2 w/o inversion without HXNS/MAQU
```{r, eval = FALSE}
admK2 = RcppCNPy::npyLoad("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/pca_admix_mme_woNorthern_thinnedsnps_noinv_k2.admix.Q.npy")
Ind.id <- read_delim("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", col_names = T, delim = "\t")
Ind.id.noNorth = filter(Ind.id, Pop != "HXNS", Pop != "MAQU")
Mme.thinned.noinv.nNorth.admix.ind = cbind(Ind.id.noNorth, admK2)

#Add latitude from population information dataframe
pop <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
pop.filt = filter(pop, Pop != "HXNS", Pop != "MAQU")
Mme.thinned.noinv.nNorth.admix.ind = left_join(Mme.thinned.noinv.nNorth.admix.ind, pop.filt, by="Pop")
#Add distance from JIGA to dataframe
dist <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Mme.thinned.noinv.nNorth.admix.ind = as_tibble(left_join(Mme.thinned.noinv.nNorth.admix.ind, dist, by="Pop"))


#Estimate the mean admixture proportion per pop
K.neutral.mean <- plyr::ddply(Mme.thinned.noinv.nNorth.admix.ind, c("Pop","Dist","lat"),
                              summarise, 
                              K1.mean = mean(`1`), 
                              K1.sd = sd(`1`))

K.neutral.mean$Pop <- ordered(K.neutral.mean$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS"))

ancK = ggplot(data = K.neutral.mean) +
  geom_smooth(aes(x=Dist, y=(1-K1.mean)), method = "loess", span = 0.5) +
  geom_point(aes(x=Dist, y=(1-K1.mean))) +
  geom_errorbar(aes(x=Dist, y=(1-K1.mean), ymin=(1-K1.mean)-K1.sd, ymax=(1-K1.mean)+K1.sd)) +
  xlab("Distance from southern pop [km]") +
  ylab("Southern ancestry")
ancK

"LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS"))
ordered = Mme.thinned.noinv.nNorth.admix.ind[order(Mme.thinned.noinv.nNorth.admix.ind$Pop),]
barplot(t(as.matrix(subset(ordered, select=3:4))), col=c("#05668D", "firebrick"), border=NA)
```


Combined plots of GWancestry and inversion clines
```{r, eval = FALSE}
ancK.inv.cpoint.dist = (ancK |inv4 | inv7 | inv8) / (inv11 | inv18 | inv19 | inv24)
```



Correlation between inversion freqs and ancestry
```{r, eval = FALSE}
Prop.S.Alleles.df2.filt.ancK = left_join(Prop.S.Alleles.df2.filt, K.neutral.mean, by="Pop")

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr24)) +
  geom_point() 

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr19)) +
  geom_point()

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr18)) +
  geom_point() 

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr11)) +
  geom_point() 

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr8)) +
  geom_point() 

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr7)) +
  geom_point() 

ggplot(Prop.S.Alleles.df2.filt.ancK, aes(x=(1-K1.mean), y=Prop.S.Allele.chr4)) +
  geom_point() 
```


# Association between QTL-linked inversion genotype and body size

Run GLM for body size vs inversion karyotype for all three inversions separately and only for populations that are not fixed or nearly fixed for one of the karyotypes. 

inv11: 
```{r, eval = FALSE}
inv11.pca.karyotypes.df = read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv11_ind_karyotypes_allpops.csv")

size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_data.csv", col_types = "ccdd")

inv11.pca.karyotypes.size.df = inner_join(inv11.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
inv11.pca.karyotypes.size.df$ktype <- ordered(inv11.pca.karyotypes.size.df$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv11.pca.karyotypes.size.df, aes(x=Pop, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv11 karyotype")


inv11.pca.karyotypes.size.df.filt = filter(inv11.pca.karyotypes.size.df, Pop == "DXMA" | Pop == "MBNS" | Pop == "HXNS"| Pop == "MDME")
inv11.pca.karyotypes.size.df.filt = as_tibble(inv11.pca.karyotypes.size.df.filt)
#inv11.pca.karyotypes.size.df.filt = filter(inv11.pca.karyotypes.size.df, Pop == "HXNS")

lm.fact.inv11 <- lm(StdLgth ~ ktype, data = inv11.pca.karyotypes.size.df.filt)
summary(lm.fact.inv11)

lmm.fact.inv11 <- lmer(StdLgth ~ ktype + (1 | Pop), data = inv11.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv11)
anova(lmm.fact.inv11)
report(lmm.fact.inv11)
effectsize(lmm.fact.inv11)

lmm.int.inv11 <- lmer(StdLgth ~ as.numeric(ktype.int) + (1 | Pop), data = inv11.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.int.inv11)
anova(lmm.int.inv11)
report(lmm.int.inv11)
effectsize(lmm.int.inv11)


inv11.pca.karyotypes.size.df.filt2 = inv11.pca.karyotypes.size.df.filt %>% drop_na(StdLgth)
lmm.fact.inv11.lme <- lmer(StdLgth ~ ktype+ (1 | Pop), data = inv11.pca.karyotypes.size.df.filt2)
summary(lmm.fact.inv11.lme)
anova(lmm.fact.inv11.lme)

library(nlme)
mod <- lme(StdLgth ~ ktype, random = ~1 | Pop, data = inv11.pca.karyotypes.size.df.filt2)
summary(mod)
anova(mod)


inv11.pca.karyotypes.size.df.filt$ktype <- ordered(inv11.pca.karyotypes.size.df.filt$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv11.pca.karyotypes.size.df.filt, aes(x=ktype, y=StdLgth, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = T, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv11 karyotype")

ggplot(data = inv11.pca.karyotypes.size.df.filt, aes(x=Pop, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  geom_jitter(aes(colour=Pop)) +
  scale_fill_manual(values = c("#4f000b","#FFC100","#3d5a80")) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Pop")

inv11.pca.karyotypes.sl.df.filt.dx = filter(inv11.pca.karyotypes.size.df.filt, Pop == "DXMA")
inv11.pca.karyotypes.sl.df.filt.mb = filter(inv11.pca.karyotypes.size.df.filt, Pop == "MBNS")
inv11.pca.karyotypes.sl.df.filt.hx = filter(inv11.pca.karyotypes.size.df.filt, Pop == "HXNS")
summary(aov(StdLgth ~ ktype, data = inv11.pca.karyotypes.sl.df.filt.dx))
summary(aov(StdLgth ~ ktype, data = inv11.pca.karyotypes.sl.df.filt.mb))
summary(aov(StdLgth ~ ktype, data = inv11.pca.karyotypes.sl.df.filt.hx))

#including sex as covariable
size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_sex_data.csv", col_types = "ccdd")

size.df$Pop <- ordered(size.df$Pop, levels = c("JIGA", "MCNC", "OINC", "CTVA", "PGNY", "DXMA", "MDME", "MBNS", "HXNS", "MIQB"))
ggplot(data = size.df, aes(x=Pop, y=StdLgth, fill = Sex)) +
  geom_boxplot() +
  scale_fill_manual(values = c("firebrick","steelblue")) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Pop")

ggplot(data = size.df, aes(x=Pop, y=StdLgth, fill = Sex)) +
  geom_boxplot() +
  scale_fill_manual(values = c("firebrick","steelblue")) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Pop")

inv11.pca.karyotypes.size.df = inner_join(inv11.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
inv11.pca.karyotypes.size.df.filt = filter(inv11.pca.karyotypes.size.df, Pop == "DXMA" | Pop == "MBNS" | Pop == "HXNS"| Pop == "MDME")

lmm.fact.inv11.sex <- lmer(StdLgth ~ ktype + (1 | Pop) + (1 | Sex), data = inv11.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv11.sex)
anova(lmm.fact.inv11.sex)
report(lmm.fact.inv11.sex)
effectsize(lmm.fact.inv11.sex)

inv11.pca.karyotypes.size.df.filt$ktype <- ordered(inv11.pca.karyotypes.size.df.filt$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv11.pca.karyotypes.size.df.filt, aes(x=Sex, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv11 karyotype")
```

inv18:
```{r, eval = FALSE}
inv18.pca.karyotypes.df = read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv18_ind_karyotypes_allpops.csv")

size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_data.csv", col_types = "ccdd")

inv18.pca.karyotypes.size.df = inner_join(inv18.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
ggplot(data = inv18.pca.karyotypes.size.df, aes(x=Pop, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv18 karyotype")


inv18.pca.karyotypes.size.df.filt = as_tibble(filter(inv18.pca.karyotypes.size.df, Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA"))

lm.fact.inv18 <- lm(StdLgth ~ ktype, data = inv18.pca.karyotypes.size.df.filt)
summary(lm.fact.inv18)

lmm.fact.inv18 <- lmer(StdLgth ~ ktype + (1 | Pop), data = inv18.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv18)
anova(lmm.fact.inv18)
report(lmm.fact.inv18)
effectsize(lmm.fact.inv18)

lmm.int.inv18 <- lmer(StdLgth ~ ktype.int + (1 | Pop), data = inv18.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.int.inv18)
anova(lmm.int.inv18)
report(lmm.int.inv18)
effectsize(lmm.int.inv18)


inv18.pca.karyotypes.size.df$ktype <- ordered(inv18.pca.karyotypes.size.df$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv18.pca.karyotypes.size.df, aes(x=ktype, y=StdLgth, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = T, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv18 karyotype")


#including sex as covariable
size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_sex_data.csv", col_types = "ccdd")

inv18.pca.karyotypes.size.df = inner_join(inv18.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
inv18.pca.karyotypes.size.df.filt = filter(inv18.pca.karyotypes.size.df, Pop == "LRSC" | Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")

lmm.fact.inv18.sex <- lmer(StdLgth ~ ktype + (1 | Pop) + (1 | Sex), data = inv18.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv18.sex)
anova(lmm.fact.inv18.sex)
report(lmm.fact.inv18.sex)
effectsize(lmm.fact.inv18.sex)

inv18.pca.karyotypes.size.df.filt$ktype <- ordered(inv18.pca.karyotypes.size.df.filt$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv18.pca.karyotypes.size.df.filt, aes(x=Sex, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv18 karyotype")
```


inv24: 
```{r, eval = FALSE}
inv24.pca.karyotypes.df = read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv24_ind_karyotypes_allpops.csv")

size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_data.csv", col_types = "ccdd")

inv24.pca.karyotypes.size.df = inner_join(inv24.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
ggplot(data = inv18.pca.karyotypes.size.df, aes(x=Pop, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv24 karyotype")


inv24.pca.karyotypes.size.df.filt = filter(inv24.pca.karyotypes.size.df, Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")

lm.fact <- lm(StdLgth ~ ktype * Pop, data = inv24.pca.karyotypes.size.df.filt)
summary(lm.fact)

lmm.fact.inv24 <- lmer(StdLgth ~ ktype + (1 | Pop), data = inv24.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv24)
anova(lmm.fact.inv24)
report(lmm.fact.inv24)
effectsize(lmm.fact.inv24)

lmm.int.inv24 <- lmer(StdLgth ~ as.numeric(ktype.int) + (1 | Pop), data = inv24.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.int.inv24)
anova(lmm.int.inv24)
report(lmm.int.inv24)
effectsize(lmm.int.inv24)

inv24.pca.karyotypes.size.df.filt.oinc = filter(inv24.pca.karyotypes.size.df, Pop == "CTVA")
lm.int.inv24.oinc <- lm(StdLgth ~ ktype, data = inv24.pca.karyotypes.size.df.filt.oinc)
summary(lm.int.inv24.oinc)

lmm.fact <- lmer(StdLgth ~ ktype + (1 | Pop), data = inv24.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact)
anova(lmm.fact)
report(lmm.fact)
effectsize(lmm.fact)



inv24.pca.karyotypes.size.df.filt$ktype <- ordered(inv24.pca.karyotypes.size.df.filt$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv24.pca.karyotypes.size.df.filt, aes(x=ktype, y=StdLgth, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = T, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Inv24 karyotype")

ggplot(data = inv24.pca.karyotypes.size.df.filt, aes(x=Pop, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  geom_jitter(aes(colour=Pop)) +
  scale_fill_manual(values = c("#4f000b","#FFC100","#3d5a80")) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("Pop")

#check if transcriptome based karyotyping gives the same results (res from Aryn)
size.karyo.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/silverside_bodysize_data_transcriptome_karyotypes.csv", col_types = "cccccdd")

inv24.pca.karyotypes.size.df = inner_join(inv24.pca.karyotypes.df, size.karyo.df, by=c("Ind","Pop"))
inv24.pca.karyotypes.size.df.filt = filter(inv24.pca.karyotypes.size.df, Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")

inv24.pca.karyotypes.size.df.filt$congruence = if_else(condition = inv24.pca.karyotypes.size.df.filt$ktype == inv24.pca.karyotypes.size.df.filt$Chr24.trahetcriptome, T, F)


#Include sex
#including sex as covariable
size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_sex_data.csv", col_types = "ccdd")

inv24.pca.karyotypes.size.df = inner_join(inv24.pca.karyotypes.df, size.df, by=c("Ind","Pop"))
inv24.pca.karyotypes.size.df.filt = filter(inv24.pca.karyotypes.size.df, Pop == "LRSC" | Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")


lmm.fact.inv24.sex <- lmer(StdLgth ~ ktype + (1 | Pop) + (1 | Sex), data = inv24.pca.karyotypes.size.df.filt, REML = F)
summary(lmm.fact.inv24.sex)
anova(lmm.fact.inv24.sex)
report(lmm.fact.inv24.sex)
effectsize(lmm.fact.inv24.sex)


inv24.pca.karyotypes.size.df.filt$ktype <- ordered(inv24.pca.karyotypes.size.df.filt$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv24.pca.karyotypes.size.df.filt, aes(x=Sex, y=StdLgth, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Standard length") +
  xlab("inv24 karyotype")
```



# Association between QTL-linked inversion genotype and vertebral number

Run GLM for body size vs inversion karyotype for all three inversions separately and only for populations that are not fixed or nearly fixed for one of the karyotypes. 

Run GLM for body size vs inversion karyotype for all three inversions separately and only for populations that are not fixed or nearly fixed for one of the karyotypes. 

inv11: 
```{r, eval = FALSE}
inv11.pca.karyotypes.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv11_ind_karyotypes_allpops.csv")

vn.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Silverside_Wild_PhenotypicTraits_sequenced.csv", col_types = "ccdd")


inv11.pca.karyotypes.vn.df = inner_join(inv11.pca.karyotypes.df, vn.df, by=c("Ind"))

inv11.pca.karyotypes.vn.df$Pop <- ordered(inv11.pca.karyotypes.vn.df$Pop, levels = c("JIGA", "OINC", "DXMA", "MDME", "MBNS", "HXNS"))
ggplot(data = inv11.pca.karyotypes.vn.df, aes(x=Pop, y=Vertebtral_count, fill = Sex)) +
  geom_boxplot() +
  scale_fill_manual(values = c("firebrick","steelblue")) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Pop")

inv11.pca.karyotypes.vn.df.filt = filter(inv11.pca.karyotypes.vn.df, Pop == "DXMA" | Pop == "MBNS" | Pop == "HXNS")
ggplot(data = inv11.pca.karyotypes.vn.df.filt, aes(x=Length_std, y=Vertebtral_count, colour=Sex)) + geom_point()
summary(lm(data = inv11.pca.karyotypes.vn.df.filt, Vertebtral_count~Length_std*Sex))
inv11.pca.karyotypes.vn.df.filt2 = inv11.pca.karyotypes.vn.df.filt[,c(1,2,5,6,19,20)]
inv11.pca.karyotypes.vn.df.filt2 = na.omit(inv11.pca.karyotypes.vn.df.filt2)

lmm.fact.vn.inv11 <- lmer(Vertebtral_count ~ ktype + (1 | Pop), data = inv11.pca.karyotypes.vn.df.filt2, REML = F)
summary(lmm.fact.vn.inv11)
anova(lmm.fact.vn.inv11)
report(lmm.fact.vn.inv11)
effectsize(lmm.fact.vn.inv11)

lmm.int.vn.inv11 <- lmer(Vertebtral_count ~ ktype.int + (1 | Pop), data = inv11.pca.karyotypes.vn.df.filt2, REML = F)
summary(lmm.int.vn.inv11)
anova(lmm.int.vn.inv11)
report(lmm.int.vn.inv11)
effectsize(lmm.int.vn.inv11)


inv11.pca.karyotypes.vn.df.filt2$ktype <- ordered(inv11.pca.karyotypes.vn.df.filt2$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv11.pca.karyotypes.vn.df.filt2, aes(x=ktype, y=Vertebtral_count, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = F, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv11 karyotype")

inv11.pca.karyotypes.vn.df.filt.dx = filter(inv11.pca.karyotypes.vn.df, Pop == "DXMA")
inv11.pca.karyotypes.vn.df.filt.mb = filter(inv11.pca.karyotypes.vn.df, Pop == "MBNS")
inv11.pca.karyotypes.vn.df.filt.hx = filter(inv11.pca.karyotypes.vn.df, Pop == "HXNS")
inv11.pca.karyotypes.vn.df.filt.dx = inv11.pca.karyotypes.vn.df.filt.dx[,c(1,2,5,19)]
inv11.pca.karyotypes.vn.df.filt.mb = inv11.pca.karyotypes.vn.df.filt.mb[,c(1,2,5,19)]
inv11.pca.karyotypes.vn.df.filt.hx = inv11.pca.karyotypes.vn.df.filt.hx[,c(1,2,5,19)]
inv11.pca.karyotypes.vn.df.filt.dx = na.omit(inv11.pca.karyotypes.vn.df.filt.dx)
inv11.pca.karyotypes.vn.df.filt.mb = na.omit(inv11.pca.karyotypes.vn.df.filt.mb)
inv11.pca.karyotypes.vn.df.filt.hx = na.omit(inv11.pca.karyotypes.vn.df.filt.hx)

summary(aov(Vertebtral_count ~ ktype, data = inv11.pca.karyotypes.vn.df.filt.dx))
summary(aov(Vertebtral_count ~ ktype, data = inv11.pca.karyotypes.vn.df.filt.mb))
summary(aov(Vertebtral_count ~ ktype, data = inv11.pca.karyotypes.vn.df.filt.hx))

ggplot(data = inv11.pca.karyotypes.vn.df.filt2, aes(x=ktype, y=Vertebtral_count, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = F, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv11 karyotype")

ggplot(data = inv11.pca.karyotypes.vn.df.filt2, aes(x=Sex, y=Vertebtral_count, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv11 karyotype")
```


inv18: 
```{r, eval = FALSE}
inv18.pca.karyotypes.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv18_ind_karyotypes_allpops.csv")

vn.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Silverside_Wild_PhenotypicTraits_sequenced.csv", col_types = "ccdd")

inv18.pca.karyotypes.vn.df = inner_join(inv18.pca.karyotypes.df, vn.df, by=c("Ind"))
inv18.pca.karyotypes.vn.df$VN.corr = (inv18.pca.karyotypes.vn.df$Vertebtral_count/inv18.pca.karyotypes.vn.df$Length_std)
#inv18.pca.karyotypes.vn.df.filt = filter(inv18.pca.karyotypes.vn.df, Pop == "LRSC" | Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")
inv18.pca.karyotypes.vn.df.filt = filter(inv18.pca.karyotypes.vn.df, Pop == "OINC")

#raw VN
inv18.pca.karyotypes.vn.df.filt2 = inv18.pca.karyotypes.vn.df.filt[,c(1,2,5,6,19,20)]
inv18.pca.karyotypes.vn.df.filt2 = na.omit(inv18.pca.karyotypes.vn.df.filt2)

inv18.vn.aov = aov(data = inv18.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype)
summary(inv18.vn.aov)
report(inv18.vn.aov)

inv18.int.vn.aov = lm(data = inv18.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype.int)
summary(inv18.int.vn.aov)
report(inv18.int.vn.aov)



inv18.pca.karyotypes.vn.df.filt2$ktype <- ordered(inv18.pca.karyotypes.vn.df.filt2$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#FFC100","#3d5a80","#4f000b") 

ggplot(data = inv18.pca.karyotypes.vn.df.filt2, aes(x=ktype, y=Vertebtral_count, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = F, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv18 karyotype")

#incl Sex
summary(aov(data = inv18.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype*Sex))

inv18.pca.karyotypes.vn.df.filt2$ktype <- ordered(inv18.pca.karyotypes.vn.df.filt2$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#FFC100","#3d5a80","#4f000b") 
ggplot(data = inv18.pca.karyotypes.vn.df.filt2, aes(x=Sex, y=Vertebtral_count, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv18 karyotype")
```


inv24: 
```{r, eval = FALSE}
inv24.pca.karyotypes.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Inv24_ind_karyotypes_allpops.csv")

vn.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Silverside_Wild_PhenotypicTraits_sequenced.csv", col_types = "ccdd")

inv24.pca.karyotypes.vn.df = inner_join(inv24.pca.karyotypes.df, vn.df, by=c("Ind"))
inv24.pca.karyotypes.vn.df$VN.corr = (inv24.pca.karyotypes.vn.df$Vertebtral_count/inv24.pca.karyotypes.vn.df$Length_std)
#inv24.pca.karyotypes.vn.df.filt = filter(inv24.pca.karyotypes.vn.df, Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")
inv24.pca.karyotypes.vn.df.filt = filter(inv24.pca.karyotypes.vn.df,  Pop == "OINC")
ggplot(data = inv24.pca.karyotypes.vn.df.filt, aes(x=Length_std, y=Vertebtral_count)) + geom_point()
summary(lm(data = inv24.pca.karyotypes.vn.df.filt, Vertebtral_count~Length_std))

inv24.pca.karyotypes.vn.df.filt2 = inv24.pca.karyotypes.vn.df.filt[,c(1,2,5,6,19,20)]
inv24.pca.karyotypes.vn.df.filt2 = na.omit(inv24.pca.karyotypes.vn.df.filt2)

inv24.vn.aov = aov(lm(data = inv24.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype))
summary(inv24.vn.aov)
report(inv24.vn.aov)

inv24.int.vn.aov = lm(data = inv24.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype.int)
summary(inv24.int.vn.aov)
report(inv24.int.vn.aov)

inv24.pca.karyotypes.vn.df.filt2$ktype <- ordered(inv24.pca.karyotypes.vn.df.filt2$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv24.pca.karyotypes.vn.df.filt2, aes(x=ktype, y=Vertebtral_count, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = T, colour = "white", vn = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv24 karyotype")



lmm.fact.vn.inv24<- lmer(Vertebtral_count ~ ktype + (1 | Pop), data = inv24.pca.karyotypes.vn.df.filt, REML = F)
summary(lmm.fact.vn.inv11)
anova(lmm.fact.vn.inv11)
report(lmm.fact.vn.inv11)
effectsize(lmm.fact.vn.inv11)



#incl Sex
summary(aov(data = inv24.pca.karyotypes.vn.df.filt2, formula = Vertebtral_count ~ ktype*Sex))

inv24.pca.karyotypes.vn.df.filt2$ktype <- ordered(inv24.pca.karyotypes.vn.df.filt2$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#FFC100","#3d5a80","#4f000b") 
ggplot(data = inv24.pca.karyotypes.vn.df.filt2, aes(x=Sex, y=Vertebtral_count, fill = ktype)) +
  geom_boxplot() +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("Inv24 karyotype")




#size-corrected VN
inv24.pca.karyotypes.vn.df.filt3 = inv24.pca.karyotypes.vn.df.filt[,c(1,2,5,26)]
inv24.pca.karyotypes.vn.df.filt3 = na.omit(inv24.pca.karyotypes.vn.df.filt3)

summary(aov(data = inv24.pca.karyotypes.vn.df.filt3, formula = VN.corr ~ ktype))

inv24.pca.karyotypes.vn.df.filt3$ktype <- ordered(inv24.pca.karyotypes.vn.df.filt3$ktype, levels = c("south", "het", "north"))
mme.pal <- c("#4f000b","#FFC100","#3d5a80") 

ggplot(data = inv24.pca.karyotypes.vn.df.filt3, aes(x=ktype, y=VN.corr, fill = ktype)) +
  geom_violin(colour = "white") +
  geom_boxplot(width = 0.25, notch = F, colour = "white", size = 2) +
  scale_fill_manual(values = mme.pal) +
  theme_cowplot() +
  ylab("Vertebtral Count (size-corrected)") +
  xlab("Inv24 karyotype")



#check if transcriptome based karyotyping gives the same results (res from Aryn)
vn.karyo.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodyvn_associaton/silverside_bodyvn_data_transcriptome_karyotypes.csv", col_types = "cccccdd")

inv24.pca.karyotypes.vn.df = inner_join(inv24.pca.karyotypes.df, vn.karyo.df, by=c("Ind","Pop"))
inv24.pca.karyotypes.vn.df.filt = filter(inv24.pca.karyotypes.vn.df, Pop == "MCNC" | Pop == "OINC" | Pop =="CTVA")

inv24.pca.karyotypes.vn.df.filt$congruence = if_else(condition = inv24.pca.karyotypes.vn.df.filt$ktype == inv24.pca.karyotypes.vn.df.filt$Chr24.trahetcriptome, T, F)
```




# HZAR Geographic cline analysis:


### Fit sigmoidal clines to genotype and trait data:

Genome-wide ancestry
```{r}
admK2 = npyLoad("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/pca_admix_mme_woNorthern_thinnedsnps_noinv_k2.admix.Q.npy")
admK2 = npyLoad("~/Desktop/pca_admix_mme_woNorthern_thinnedsnps_noinv_k2.admix.Q.npy")

Ind.id <- read_delim("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", col_names = T, delim = "\t")
Ind.id.noNorth = filter(Ind.id, Pop != "HXNS", Pop != "MAQU")
Mme.thinned.noinv.nNorth.admix.ind = cbind(Ind.id.noNorth, admK2)
pop <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
pop.filt = filter(pop, Pop != "HXNS", Pop != "MAQU")
Mme.thinned.noinv.nNorth.admix.ind = left_join(Mme.thinned.noinv.nNorth.admix.ind, pop.filt, by="Pop")
#Add distance from JIGA to dataframe
dist <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Mme.thinned.noinv.nNorth.admix.ind = left_join(Mme.thinned.noinv.nNorth.admix.ind, dist, by="Pop")
Mme.thinned.noinv.nNorth.admix.ind.df = Mme.thinned.noinv.nNorth.admix.ind[,c(2,3,7)]
names(Mme.thinned.noinv.nNorth.admix.ind.df) = c("Pop", "K","Dist")
Mme.thinned.noinv.nNorth.admix.ind.df$Dist = Mme.thinned.noinv.nNorth.admix.ind.df$Dist + 1
Mme.thinned.noinv.nNorth.admix.ind.df$K = 1- Mme.thinned.noinv.nNorth.admix.ind.df$K

#Estimate the mean admixture proportion per pop
K.neutral.mean <- plyr::ddply(Mme.thinned.noinv.nNorth.admix.ind.df, c("Pop","Dist"),
                              summarise, 
                              K1.mean = mean(K), 
                              K1.sd = sd(K))

K.neutral.mean$Pop <- ordered(K.neutral.mean$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS"))

#find the parameters for the equation
plot(K.neutral.mean$Dist, K.neutral.mean$K1.mean)

#Different way:
summary(mod1<-nls(K1.mean ~ SSlogis( log(Dist), Asym, xmid, scal),data=K.neutral.mean))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(K.neutral.mean, plot(Dist,K1.mean))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="Genome-wide ancestry",xlab="Distance")
with(K.neutral.mean, matpoints(Dist,K1.mean,pch=1))
```

Inv24
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1

#find the parameters for the equation
SS<-getInitial(Prop.S.Allele.chr24~SSlogis(Dist,alpha,xmid,scale),data=Prop.S.Alleles.df2.filt)
#we used a different parametrization
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<-SS["alpha"]/(exp(SS["xmid"]/SS["scale"])+1)
#the formula for the model
dist = Prop.S.Alleles.df2.filt$Dist
inv24 = Prop.S.Alleles.df2.filt$Prop.S.Allele.chr24
log_formula<-formula(inv24~K*N0*exp(R*dist)/(K+N0*(exp(R*dist)-1)))
#fit the model
m<-nls(log_formula,start=list(K=K_start,R=R_start,N0=N0_start))
#estimated parameters
summary(m)
#get some estimation of goodness of fit
cor(inv24,predict(m))
plot(Prop.S.Alleles.df2.filt$Dist,Prop.S.Alleles.df2.filt$Prop.S.Allele.chr24)
lines(dist,predict(m),col="red",lty=2,lwd=3)


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr24 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr24))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="inv24 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr24,pch=1))
```


Inv18
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1

#find the parameters for the equation
SS<-getInitial(Prop.S.Allele.chr18~SSlogis(Dist,alpha,xmid,scale),data=Prop.S.Alleles.df2.filt)
#we used a different parametrization
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<-SS["alpha"]/(exp(SS["xmid"]/SS["scale"])+1)
#the formula for the model
dist = Prop.S.Alleles.df2.filt$Dist
inv18 = Prop.S.Alleles.df2.filt$Prop.S.Allele.chr18
log_formula<-formula(inv18~K*N0*exp(R*dist)/(K+N0*(exp(R*dist)-1)))
#fit the model
m<-nls(log_formula,start=list(K=K_start,R=R_start,N0=N0_start))
#estimated parameters
summary(m)
#get some estimation of goodness of fit
cor(inv18,predict(m))
plot(Prop.S.Alleles.df2.filt$Dist,Prop.S.Alleles.df2.filt$Prop.S.Allele.chr18)
lines(dist,predict(m),col="red",lty=2,lwd=3)


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr18 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr18))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="inv18 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr18,pch=1))
```

Inv19
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr19 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr19))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.9195))),
type="l",lty=c(1,3,3),ylab="inv19 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr19,pch=1))
```

Inv11
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr11 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr11))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.9115))),
type="l",lty=c(1,3,3),ylab="inv11 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr11,pch=1))
```

Inv4
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr4 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr4))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="inv4 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr4,pch=1))
```

Inv7
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr7 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr7))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="inv7 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr7,pch=1))
```

Inv8
```{r}
Prop.S.Alleles.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_associaton/InvFreq_southernAllele_allpops.csv")
#Add latitude from population information dataframe
pop <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/silverside_popsamples_coords.csv")
names(pop)[1] = "Pop"
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df, pop, by="Pop")
#Add distance from JIGA to dataframe
dist <- read.csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
Prop.S.Alleles.df2 = left_join(Prop.S.Alleles.df2, dist, by="Pop")
Prop.S.Alleles.df2 = type_convert(Prop.S.Alleles.df2)
Prop.S.Alleles.df2.filt = filter(Prop.S.Alleles.df2, Pop != "HXNS", Pop != "MAQU")
Prop.S.Alleles.df2.filt$Dist = Prop.S.Alleles.df2.filt$Dist + 1


#Different way:
summary(mod1<-nls(Prop.S.Allele.chr8 ~ SSlogis( log(Dist), Asym, xmid, scal),data=Prop.S.Alleles.df2.filt))

Dist_x <- seq(2, 2315, length = 100)

predict(mod1, data.frame(Dist = Dist_x))

with(Prop.S.Alleles.df2.filt, plot(Dist,Prop.S.Allele.chr8))

lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))

se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))

###plot points and curve plus ci's
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.985))),
type="l",lty=c(1,3,3),ylab="inv8 frequency",xlab="Distance")
with(Prop.S.Alleles.df2.filt, matpoints(Dist,Prop.S.Allele.chr8,pch=1))
```


### Fit sigmodal clines to phenotypic trait values

Growth rate at 15C and 28C, and vertebral number
```{r}
mme.traits = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/phenotype_data/Mme_mean_traitvalues_hice_etal_2012.csv")
mme.traits.noNorth = filter(mme.traits, pop != "HXNS", pop != "MAQU")
names(mme.traits.noNorth)[1] = "Pop"

#Add distance
dist <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
mme.traits.noNorth = left_join(mme.traits.noNorth, dist, by="Pop")
mme.traits.noNorth$Dist = mme.traits.noNorth$Dist + 1

mme.traits.noNorth$Pop <- ordered(mme.traits.noNorth$Pop, levels = c("JIGA", "LRSC", "MCNC", "OINC", "CTVA", "PANY", "MCCT", "DXMA", "MDME", "MBNS"))

#GR15
plot(mme.traits.noNorth$Dist, mme.traits.noNorth$gr15.mean)
summary(mod1<-nls(gr15.mean ~ SSlogis( log(Dist), Asym, xmid, scal),data=mme.traits.noNorth))
Dist_x <- seq(0, 2315, length = 100)
predict(mod1, data.frame(Dist = Dist_x))
with(mme.traits.noNorth, plot(Dist,gr15.mean))
lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))
se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="GR @ 15C",xlab="Distance")
with(mme.traits.noNorth, matpoints(Dist,gr15.mean,pch=1))

SS<-getInitial(gr15.mean~SSlogis(Dist,alpha,xmid,scale),data=mme.traits.noNorth)
#we used a different parametrization
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<-SS["alpha"]/(exp(SS["xmid"]/SS["scale"])+1)
#the formula for the model
dist = mme.traits.noNorth$Dist + 1
gr15 = mme.traits.noNorth$gr15.mean
log_formula<-formula(gr15~K*N0*exp(R*dist)/(K+N0*(exp(R*dist)-1)))
#fit the model
m<-nls(log_formula,start=list(K=K_start,R=R_start,N0=N0_start))
#estimated parameters
summary(m)
#get some estimation of goodness of fit
cor(gr15,predict(m))
plot(mme.traits.noNorth$Dist,mme.traits.noNorth$gr15.mean)
lines(dist,predict(m),col="red",lty=2,lwd=3)

#GR28
plot(mme.traits.noNorth$Dist, mme.traits.noNorth$gr28.mean)
summary(mod1<-nls(gr28.mean ~ SSlogis( log(Dist), Asym, xmid, scal),data=mme.traits.noNorth))
Dist_x <- seq(0, 2328, length = 100)
predict(mod1, data.frame(Dist = Dist_x))
with(mme.traits.noNorth, plot(Dist,gr28.mean))
lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))
se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="GR @ 28C",xlab="Distance")
with(mme.traits.noNorth, matpoints(Dist,gr28.mean,pch=1))

SS<-getInitial(gr28.mean~SSlogis(Dist,alpha,xmid,scale),data=mme.traits.noNorth)
#we used a different parametrization
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<-SS["alpha"]/(exp(SS["xmid"]/SS["scale"])+1)
#the formula for the model
dist = mme.traits.noNorth$Dist + 1
gr28 = mme.traits.noNorth$gr28.mean
log_formula<-formula(gr28~K*N0*exp(R*dist)/(K+N0*(exp(R*dist)-1)))
#fit the model
m<-nls(log_formula,start=list(K=K_start,R=R_start,N0=N0_start))
#estimated parameters
summary(m)
#get some estimation of goodness of fit
cor(gr28,predict(m))
plot(mme.traits.noNorth$Dist,mme.traits.noNorth$gr28.mean)
lines(dist,predict(m),col="red",lty=2,lwd=3)

#VN
plot(mme.traits.noNorth$Dist, mme.traits.noNorth$vn.mean)
summary(mod1<-nls(vn.mean ~ SSlogis( log(Dist), Asym, xmid, scal),data=mme.traits.noNorth))
Dist_x <- seq(0, 2328, length = 100)
predict(mod1, data.frame(Dist = Dist_x))
with(mme.traits.noNorth, plot(Dist,vn.mean))
lines(press_x, predict(mod1, data.frame(Dist = Dist_x)))
se.fit <- sqrt(apply(attr(predict(mod1, data.frame(Dist = Dist_x)),"gradient"),1,
function(x) sum(vcov(mod1)*outer(x,x))))
matplot(Dist_x, predict(mod1, data.frame(Dist = Dist_x)) + outer(se.fit,qnorm(c(.5, .025,.975))),
type="l",lty=c(1,3,3),ylab="VN",xlab="Distance")
with(mme.traits.noNorth, matpoints(Dist,vn.mean,pch=1))

#find the parameters for the equation
SS<-getInitial(vn.mean~SSlogis(Dist,alpha,xmid,scale),data=mme.traits.noNorth)
#we used a different parametrization
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<-SS["alpha"]/(exp(SS["xmid"]/SS["scale"])+1)
#the formula for the model
dist = mme.traits.noNorth$Dist + 1
VN = mme.traits.noNorth$vn.mean
log_formula<-formula(VN~K*N0*exp(R*dist)/(K+N0*(exp(R*dist)-1)))
#fit the model
m<-nls(log_formula,start=list(K=K_start,R=R_start,N0=N0_start))
#estimated parameters
summary(m)
#get some estimation of goodness of fit
cor(VN,predict(m))
plot(mme.traits.noNorth$Dist,mme.traits.noNorth$vn.mean)
lines(dist,predict(m),col="red",lty=2,lwd=3)
```



Perform the cline analyses without samples from MAQU and HXNS as they have different genomic ancestries, complicating the interpretation of the results and comparability to neutral genetic ancestries. 

```{r, eval = FALSE}
setwd("/workdir/arne/results/selection/hzar_cline_analysis/cline-analysis")

install.packages("hzar")
library("hzar")
install.packages("subplex")
library("subplex")
install.packages("doParallel")
library("doParallel")
install.packages("plotrix")
library("plotrix")

source("runHZAR.R")
source("/workdir/arne/results/selection/hzar_cline_analysis/HZAR_Script_for_output_results.R")
```


Plot distribution in cline centres and cline widths  95% CIs
```{r, eval = FALSE}
hzar.inv.res = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/inversion_ancestry_clines/hzar_cline_analysis/hzar_inv_result_table_v1.csv")

hzar.inv.res.filt = filter(hzar.inv.res, marker == "GWanc" | marker == "inv11" | marker == "inv18" | marker == "inv24")
hzar.inv.res.filt$marker = with(hzar.inv.res.filt, reorder("inv11", "inv18", "inv24", "GWanc"))
hzar.inv.res.filt$marker <- factor(hzar.inv.res.filt$marker,levels = c("inv11", "inv18", "inv24", "GWanc"))

ggplot(data = hzar.inv.res.filt, aes(x = marker, y=center, ymin=lowerC, ymax=upperC, fill=marker)) + geom_pointrange(stroke=1, size=1, shape=21) + theme_cowplot()

ggplot(data = hzar.inv.res.filt, aes(x = marker, y=width, ymin=lowerW, ymax=upperW, fill=marker)) + geom_pointrange(stroke=1, size=1, shape=21) + theme_cowplot()
```


Plot cline centres onto latitudinal changes in environmental variables
```{r, eval=F}
ggplot(data = Mme.envdata.dist) +
  geom_smooth(aes(x=Dist, y=lt_meanSST), method = "loess", span=0.5, colour = "gray50") +
  geom_smooth(aes(x=Dist, y=lt_max_SST), method = "loess", span=0.5, colour = "gray20") +
  geom_smooth(aes(x=Dist, y=lt_minSST), method = "loess", span=0.5, colour = "gray70") +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")

ggplot(data = Mme.envdata.dist) +
  geom_smooth(aes(x=Dist, y=seasonality_degC), method = "loess", span=0.5, colour = "gray70") +
  geom_smooth(aes(x=Dist, y=BO2_temprange_ss, method = "loess", span=0.5), colour = "gray20") +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")

ggplot(data = Mme.envdata.dist) +
  geom_smooth(aes(x=Dist, y=n.weeks.above12_meanSST, method = "loess", span=0.5), colour = "gray50") +
  geom_smooth(aes(x=Dist, y=n.weeks.above12_minSST, method = "loess", span=0.5), colour = "gray20")  +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")

ggplot(data = Mme.envdata.dist) +
  geom_smooth(aes(x=Dist, y=BO2_tempmean_ss, method = "loess", span=0.5), colour = "gray50") +
  geom_smooth(aes(x=Dist, y=BO2_temprange_ss, method = "loess", span=0.5), colour = "gray20") +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")

ggplot(data = Mme.envdata.dist) +
  geom_smooth(aes(x=Dist, y=BO2_tempmean_ss, method = "loess", span=0.5), colour = "gray50") +
  geom_smooth(aes(x=Dist, y=BO2_tempmin_ss, method = "loess", span=0.5), colour = "gray20") +
  geom_smooth(aes(x=Dist, y=BO2_tempmax_ss, method = "loess", span=0.5), colour = "gray70") +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")


pca.env.pcs = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/Mme_cline_environmental_variables_BioOracle_addHBdata_PCAscores.csv")
dist <- read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/geographic_environmental_data/leastcost_geographic_geodist_fromJIGA.csv")
names(dist)[1] = "pop"
pca.env.pcs.dist = left_join(pca.env.pcs, dist, by="pop")
pca.env.pcs.dist$Dist = pca.env.pcs.dist$Dist + 1

ggplot(data = pca.env.pcs.dist) +
  geom_smooth(aes(x=Dist, y=-PC1), method = "loess", span=0.5, colour = "firebrick") + 
  geom_smooth(aes(x=Dist, y=PC2), method = "loess", span=0.5, colour = "gray30") +
  geom_vline(data = hzar.inv.res, aes(xintercept=center, colour = marker)) +
  geom_vline(data = hzar.inv.res, aes(xintercept=lowerC, colour = marker), linetype = "dashed") +
  geom_vline(data = hzar.inv.res, aes(xintercept=upperC, colour = marker), linetype = "dashed")
```






Compare clines between inversions and genome-wide ancestry: use script from https://github.com/seanstankowski/Heliconius_MS/blob/master/Comaring_linear_and_quadratic_fits.txt

Inv24 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr24 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv24", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```

Inv19 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr19 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv19", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```

Inv18 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr18 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv18", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```


Inv11 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr11 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv11", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```


Inv8 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr8 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv8", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```


Inv7 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr7 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv7", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```


Inv4 vs GWancestry
```{r, eval=F}
#Make dataframe for all inversions and ancestry
data.df = inner_join(K.neutral.mean, Prop.S.Alleles.df2.filt, by=c("Pop","Dist"))

	###define trait variables, x and y
y_trait <- data.df$K1.mean ##define a variable for yb...
y_trait2 <- y_trait^2 ## ...and y squared 
x_trait <- data.df$Prop.S.Allele.chr4 ##define x_trait
	
##define and fit the quadratic
quadratic.model <- lm(x_trait ~ y_trait + y_trait2) ## define and fit the quadratic model
## Solve a vector of values predicted from values so  plot the curve
min <- min(y_trait, na.rm = T) ## find the min of trait_x
max <- max(y_trait, na.rm = T) ## find the max of trait_x
y_trait_values <- seq(min, max, 0.001) ##make the vector of 1 k numbers spanning x_min and x_max
predictedvalues <- predict(quadratic.model,list(y_trait=y_trait_values, y_trait2=y_trait_values^2)) ##predict using quadratic model
## make a plot
plot(x_trait,y_trait, xlab = "Southern Ancestry", ylab = "Frequency of inv4", cex=2)
lines(predictedvalues, y_trait_values, col = "red", lwd = 3) ## add the quadratic fit to 	
### Linear_Fit
linear.model <- lm(x_trait~y_trait)
abline(lm(y_trait~x_trait),  col = "blue", lwd = 3) ## add linear model to the plot
### Summary of model fits	
summary(linear.model)
summary(quadratic.model) ## summary of the quadratic model
### Compare models using F-ratio with anova		
anova(linear.model, quadratic.model)
```


# Estimating strength of selection on inversions
```{r, eval=F}
s* = [(1.782 * o)/w]^2

s* is mean strength of effective selection
o is dispersal distance (#0 - 50km for silverside in year class 1; estimate from Clarke et al. 2010 Ecology, 91(12))
w is cline width



#Inv24
o=5
w=697.4756005
LowW=574.3576308
HighW=850.4538859
s.inv24.mean = ((1.782*o)/w)^2
s.inv24.low = ((1.782*o)/LowW)^2
s.inv24.high = ((1.782*o)/HighW)^2

#Inv19
o=25
w=594.519109		
LowW=493.185326
HighW=717.0136248
s.inv19.mean = ((1.782*o)/w)^2
s.inv19.low = ((1.782*o)/LowW)^2
s.inv19.high = ((1.782*o)/HighW)^2

#Inv18
o=25
w=428.0151153		
LowW=301.4150328
HighW=585.0208771	
s.inv18.mean = ((1.782*o)/w)^2
s.inv18.low = ((1.782*o)/LowW)^2
s.inv18.high = ((1.782*o)/HighW)^2

#Inv11
o=25
w=339.5763887		
LowW=240.6184577
HighW=494.6413334
s.inv11.mean = ((1.782*o)/w)^2
s.inv11.low = ((1.782*o)/LowW)^2
s.inv11.high = ((1.782*o)/HighW)^2

#Inv8
o=25
w=280.6710454		
LowW=67.22965391
HighW=623.6772554
s.inv8.mean = ((1.782*o)/w)^2
s.inv8.low = ((1.782*o)/LowW)^2
s.inv8.high = ((1.782*o)/HighW)^2

#Inv7
o=25
w=656.8538051				
LowW=536.642637
HighW=801.7204709
s.inv7.mean = ((1.782*o)/w)^2
s.inv7.low = ((1.782*o)/LowW)^2
s.inv7.high = ((1.782*o)/HighW)^2

#Inv4
o=25
w=702.1073476					
LowW=589.1537033
HighW=839.5015785
s.inv4.mean = ((1.782*o)/w)^2
s.inv4.low = ((1.782*o)/LowW)^2
s.inv4.high = ((1.782*o)/HighW)^2
```


## Estimte s* for inversions but permutate over different dispersal distances
```{r, eval=F}
#Create a fake negative binomial distribution between 0 and 50
n = rnorm(1000, 0, 15)
hist(n,                                          # Plot of randomly drawn nbinom density
     breaks = 100,
     main = "")
n.df = as.data.frame(n)
n.df = abs(n.df)
hist(n.df$n,                                          # Plot of randomly drawn nbinom density
     breaks = 100,
     main = "")
mean(n.df$n)

#Iterate over dispersal distances drawn from distribution. 1000 iterations

## Inv24
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=697.4756005
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv24.mean = (((1.782*o)/w)^2)
  write(paste(s.inv24.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv24_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv24 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv24_out.txt") 
hist(perm.sel.inv24$V1)
mean.s.inv24 = mean(perm.sel.inv24$V1)
sd.s.inv24 = sd(perm.sel.inv24$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv24$V1, ci = 0.95)


## inv19
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=594.519109
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv19.mean = (((1.782*o)/w)^2)
  write(paste(s.inv19.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv19_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv19 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv19_out.txt") 
hist(perm.sel.inv19$V1)
mean.s.inv19 = mean(perm.sel.inv19$V1)
sd.s.inv19 = sd(perm.sel.inv19$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv19$V1, ci = 0.95)

## inv18
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=428.0151153
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv18.mean = (((1.782*o)/w)^2)
  write(paste(s.inv18.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv18_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv18 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv18_out.txt") 
hist(perm.sel.inv18$V1)
mean.s.inv18 = mean(perm.sel.inv18$V1)
sd.s.inv18 = sd(perm.sel.inv18$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv18$V1, ci = 0.95)


## inv11
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=339.5763887
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv11.mean = (((1.782*o)/w)^2)
  write(paste(s.inv11.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv11_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv11 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv11_out.txt") 
hist(perm.sel.inv11$V1)
mean.s.inv11 = mean(perm.sel.inv11$V1)
sd.s.inv11 = sd(perm.sel.inv11$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv11$V1, ci = 0.95)


## inv8
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=280.6710454
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv8.mean = (((1.782*o)/w)^2)
  write(paste(s.inv8.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv8_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv8 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv8_out.txt") 
hist(perm.sel.inv8$V1)
mean.s.inv8 = mean(perm.sel.inv8$V1)
sd.s.inv8 = sd(perm.sel.inv8$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv8$V1, ci = 0.95)

## inv7
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=656.8538051
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv7.mean = (((1.782*o)/w)^2)
  write(paste(s.inv7.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv7_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv7 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv7_out.txt") 
hist(perm.sel.inv7$V1)
mean.s.inv7 = mean(perm.sel.inv7$V1)
sd.s.inv7 = sd(perm.sel.inv7$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv7$V1, ci = 0.95)


## inv4
n.vec = c(n.df$n)
x <- 1
z <- 1000 #number of permutations
w=702.1073476
repeat {
  o <- sample(n.vec, 1, replace = T) #resampling step
  s.inv4.mean = (((1.782*o)/w)^2)
  write(paste(s.inv4.mean), "~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv4_out.txt", append=T, ) # append output to file. If you re-run the script, you have to delete this file first from the folder or rename the output file
  x = x+1 #add next round
  if (x == z){ #stop if reaches number of permutations (z)
    break
  }
}

#read output script for downstream analyses
perm.sel.inv4 <- read.table("~/Dropbox/Cornell_Postdoc/analysis/results/perm_cline_selection_inv4_out.txt") 
hist(perm.sel.inv4$V1)
mean.s.inv4 = mean(perm.sel.inv4$V1)
sd.s.inv4 = sd(perm.sel.inv4$V1)
CI_z <- function (x, ci = 0.95)
{
`%>%` <- magrittr::`%>%`
standard_deviation <- sd(x)
sample_size <- length(x)
Margin_Error <- abs(qnorm((1-ci)/2))* standard_deviation/sqrt(sample_size)
df_out <- data.frame( sample_size=length(x), Mean=mean(x), sd=sd(x),
Margin_Error=Margin_Error,
'CI lower limit'=(mean(x) - Margin_Error),
'CI Upper limit'=(mean(x) + Margin_Error)) %>%
tidyr::pivot_longer(names_to = "Measurements", values_to ="values", 1:6 )
return(df_out)
}
CI_z(perm.sel.inv4$V1, ci = 0.95)
```





#Plot inversion cline widths, cline centres and selection coefficient for each inversion

```{r, eval=F}
hzar.res.df = read_csv("~/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/inversion_ancestry_clines/hzar_cline_analysis/hzar_inv_result_table_v1.csv")

hzar.res.df$marker <- ordered(hzar.res.df$marker, levels = c("inv4", "inv7", "inv8", "inv11", "inv18", "inv19", "inv24", "GWanc"))

c.plot = ggplot(data = hzar.res.df, aes(x=marker, y=center, colour=marker)) +
  geom_point() +
  geom_pointrange(aes(ymin=center-lowerC, ymax=center+upperC)) +
  scale_colour_manual(values = c("#941322","#FF7B00","#468100","#007FFF","#8C3FD3","#FFC400","#00C5FF","grey60")) +
  ylab("cline center [km]") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.title.x = element_blank())
  
w.plot = ggplot(data = hzar.res.df, aes(x=marker, y=width, colour=marker)) +
  geom_point() +
  geom_pointrange(aes(ymin=width-lowerW, ymax=width+upperW)) +
  scale_colour_manual(values = c("#941322","#FF7B00","#468100","#007FFF","#8C3FD3","#FFC400","#00C5FF","grey60")) +
  ylab("cline width [km]") +
  theme_cowplot() +
  theme(legend.position="none",
        axis.title.x = element_blank())

s.plot = ggplot(data = hzar.res.df, aes(x=marker, y=s.mean.perm, colour=marker)) +
  geom_point() +
  geom_pointrange(aes(ymin=s.mean.perm-s.mean.perm.CI.lower, ymax=s.mean.perm+s.mean.perm.CI.upper)) +
  scale_colour_manual(values = c("#941322","#FF7B00","#468100","#007FFF","#8C3FD3","#FFC400","#00C5FF","grey60")) +
  ylab("s*") +
  xlab("Genomic region") +
  theme_cowplot() +
  theme(legend.position="none")

cline.plots = c.plot / w.plot / s.plot
```





### Cline on chr13 and chr17


#### Chr13
```{r message=F, warning=F}
Ind.id <- read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
```

```{bash eval=F, include=T}
## subset outlier
cat mme_all_filtsnps_beagleGL_Mme_chr13.beagle | sed -n -e '1p' | awk '/20100602/,/22294270/' | gzip > mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle.gz
cat mme_all_filtsnps_beagleGL_Mme_chr13.beagle | awk '/Mme_chr13_20100602/,/Mme_chr13_22294270/' | gzip > mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle.gz
```

```{r message=F}
# read beagle file
VNqtl.chr13_beagle <- read_tsv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle.gz")
```

Polarize genotype probabilities
```{r}
# We will polarize by the individual that groups most extremely with early spawning on the PCA, EK2021_389
# EK2021_389 corresponds to beagle individual 220 and columns 664, 665, and 666 in full dataset
# reduce outlier beagle to first 30 row to test script
#outlier_beagle_30 <- head(outlier_beagle, 30)
```

```{r}
## Define a function to get allele dosage from genotype likelihood
get_allele_dosage <- function(x){
  if(x[2]==x[3] & x[3]==x[4]){
    return(NA) ## return NA at sites with no coverages (where rescaled GLs are 0.333, 0.333, 0.333)
  } else {
    if(x[1]>0.5) { ## polarize the GLs based on frequency at early individual
      x[2:4] <- x[4:2]
    }
    return(x[3] + 2*x[4])
  }
}

# try nicolas' and liams script for extracting allelic dosage and polarize in same step
# separate linkage group and position 
VNqtl.chr13_beagle <- VNqtl.chr13_beagle %>% separate(marker, c(NA ,"lg", "pos")) %>% 
  dplyr::select(-allele2)

# set up the data frame, ncols should equal the number of samples and nrows should equal the number of loci
dosage <- as.data.frame(matrix(ncol = (ncol(VNqtl.chr13_beagle)-3)/3+3, nrow = nrow(VNqtl.chr13_beagle)))
dosage[,1:3]=VNqtl.chr13_beagle[,1:3]

## Get allele dosage iteratively from each individual
# 4 columns are extracted for each individual. the 1st of the four columns is the GL for the major allele for the polarizing individual. Choose the reference column according to the individual you want to polarize from. In our case, that is column 199 (EK2021_389)
for (j in 1:((ncol(VNqtl.chr13_beagle)-3)/3)){
  temp_ind <- VNqtl.chr13_beagle[,c(142, (1+3*j):(3+3*j))]
  dosage[,3+j] <- apply(temp_ind, 1, get_allele_dosage)
}

# rename columns to match sample names

colnames(dosage) <- c("chr","pos","V3",Ind.id$Ind)
```

#### Convert to long format for plotting

```{r}
 dosage_long<- pivot_longer(dosage, cols = 4:ncol(dosage), names_to = "Ind", values_to = "allele_dosage") %>% 
  dplyr::select(-V3) 

dosage_long = left_join(dosage_long, Ind.id, by = "Ind")

write_tsv(dosage_long, "~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle_alleledosage.txt")
```

## Plot genotype heatmaps
```{r}
dosage_long <- read_tsv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle_alleledosage.txt")

dosage_long$Pop <- ordered(dosage_long$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))

dosage_long_plot <- dosage_long %>% 
  mutate(allele_dosage_rounded = as.character(round(allele_dosage))) %>% 
  ggplot(aes(x=as_factor(pos), y=Ind, fill = allele_dosage_rounded)) +
  geom_tile() +
  scale_fill_viridis_d(direction = 1) +
  facet_grid(Pop~chr, scales = "free", space = "free") +
  theme_bw() +
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.margin.x = unit(0.2, "lines"),
        strip.text.y = element_text(angle = 0))
dosage_long_plot
```



```{r}
## define populations based on genotype and join with sample table
genotype_assn <- dosage_long %>% 
  group_by(Ind) %>% 
  summarise(avg_dosage = mean(allele_dosage, na.rm = T))

genotype_assn.id <- Ind.id %>% left_join(genotype_assn, by = "Ind")
write_tsv(genotype_assn.id, "~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr13.VNqtl.beagle_alleledosage_avg_byind.txt")
```

Correlation between chr13 allele dosage and VN number
```{r}
vn.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Silverside_Wild_PhenotypicTraits_sequenced.csv", col_types = "ccdd")

chr13.vnqt.alleledosage.vn.df = inner_join(genotype_assn.id, vn.df, by=c("Ind"))

chr13.vnqt.alleledosage.vn.df$Pop <- ordered(chr13.vnqt.alleledosage.vn.df$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))

chr13.vnqt.alleledosage.vn.plot = ggplot(data = chr13.vnqt.alleledosage.vn.df, aes(x=Pop, y=avg_dosage)) +
  geom_boxplot() +
  geom_hline(yintercept = mean(chr13.vnqt.alleledosage.vn.df$avg_dosage)) +
  ylim(c(0,2)) +
  scale_fill_manual(values = c("firebrick","steelblue")) +
  theme_cowplot() +
  ylab("Mean allele dosage") +
  xlab("Pop")

ggplot(data = chr13.vnqt.alleledosage.vn.df, aes(x=round(avg_dosage,digits = 0), y=Vertebtral_count)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_cowplot() +
  ylab("Vertebtral Count") +
  xlab("chr13")
```

Sum allele dosage
```{r}
## define populations based on genotype and join with sample table
genotype_assn.sum.chr13 <- dosage_long %>% 
  group_by(Ind) %>% 
  summarise(avg_dosage = sum(allele_dosage, na.rm = T))
genotype_assn.sum.chr13.id <- Ind.id %>% left_join(genotype_assn.sum.chr13, by = "Ind")

vn.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/Silverside_Wild_PhenotypicTraits_sequenced.csv", col_types = "ccdd")

chr13.sum.size.alleledosage.df = inner_join(genotype_assn.sum.chr13.id, vn.df, by=c("Ind"))

chr13.sum.size.alleledosage.df$Pop <- ordered(chr13.sum.size.alleledosage.df$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))
mme.pal <- c("#4f000b","#9e2a2b","#CE4257","darkorange2", "#ff9b54","#FFC100", "#edd746","#2a9d8f","#0f85a0","#05668D","#98C1d9", "#3d5a80") 

ggplot(data = chr13.sum.size.alleledosage.df.filt2, aes(y=round(avg_dosage,digits = 0), x=Vertebtral_count)) +
  geom_point(shape=21, aes(fill=Pop)) +
  geom_smooth(method = "lm", color="grey10") +
  theme_cowplot() +
  scale_fill_manual(values = mme.pal) +
  ylab("sum(allele dosage) vnQTL chr.13") +
  xlab("Vertebtral_count")

chr13.sum.size.alleledosage.df.filt = chr13.sum.size.alleledosage.df %>% drop_na(Vertebtral_count)
lmm.qtl13 <- lme(Vertebtral_count ~ avg_dosage, random=~1 | Pop, data = chr13.sum.size.alleledosage.df.filt)
summary(lmm.qtl13)
anova(lmm.qtl13)

ggplot(data = chr13.sum.size.alleledosage.df, aes(y=round(avg_dosage,digits = 0), x=Vertebtral_count)) +
  geom_point(shape=21, aes(fill=Pop)) +
  geom_smooth(method = "lm", aes(color=Pop)) +
  geom_smooth(method = "lm", color="grey40", linetype="dashed") +
  theme_cowplot() +
  ylab("sum(allele dosage) vnQTL chr.13") +
  xlab("Vertebtral_count")
```



#### Chr17
```{r message=F, warning=F}
Ind.id <- read.table("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/mme_popstructure/mme_all_popstr_table.txt", header = T)
```

```{bash eval=F, include=T}
cut -f2 mme_all_filtsnps_beagleGL_Mme_chr17.beagle > mme_all_filtsnps_beagleGL_Mme_chr17.beagle.markers.txt

cat mme_all_filtsnps_beagleGL_Mme_chr17.beagle | awk '/Mme_chr17_10000150/,/Mme_chr17_11000047/' | gzip > mme_all_filtsnps_beagleGL_Mme_chr17.GRqtl.beagle.gz
```

```{r message=F}
# read beagle file
VNqtl.chr17_beagle <- read_tsv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr17.GRqtl.beagle.gz")
```

Polarize genotype probabilities
```{r}
# We will polarize by the individual that groups most extremely with early spawning on the PCA, EK2021_389
# EK2021_389 corresponds to beagle individual 220 and columns 664, 665, and 666 in full dataset
# reduce outlier beagle to first 30 row to test script
#outlier_beagle_30 <- head(outlier_beagle, 30)
```

```{r}
## Define a function to get allele dosage from genotype likelihood
get_allele_dosage <- function(x){
  if(x[2]==x[3] & x[3]==x[4]){
    return(NA) ## return NA at sites with no coverages (where rescaled GLs are 0.333, 0.333, 0.333)
  } else {
    if(x[1]>0.5) { ## polarize the GLs based on frequency at early individual
      x[2:4] <- x[4:2]
    }
    return(x[3] + 2*x[4])
  }
}

# try nicolas' and liams script for extracting allelic dosage and polarize in same step
# separate linkage group and position 
VNqtl.chr17_beagle <- VNqtl.chr17_beagle %>% separate(marker, c(NA ,"lg", "pos")) %>% 
  dplyr::select(-allele2)

# set up the data frame, ncols should equal the number of samples and nrows should equal the number of loci
dosage.chr17 <- as.data.frame(matrix(ncol = (ncol(VNqtl.chr17_beagle)-3)/3+3, nrow = nrow(VNqtl.chr17_beagle)))
dosage.chr17[,1:3]=VNqtl.chr17_beagle[,1:3]

## Get allele dosage iteratively from each individual
# 4 columns are extracted for each individual. the 1st of the four columns is the GL for the major allele for the polarizing individual. Choose the reference column according to the individual you want to polarize from. In our case, that is column 199 (EK2021_389)
for (j in 1:((ncol(VNqtl.chr17_beagle)-3)/3)){
  temp_ind <- VNqtl.chr17_beagle[,c(144, (1+3*j):(3+3*j))]
  dosage.chr17[,3+j] <- apply(temp_ind, 1, get_allele_dosage)
}

# rename columns to match sample names

colnames(dosage.chr17) <- c("chr","pos","V3",Ind.id$Ind)
```

#### Convert to long format for plotting

```{r}
dosage.chr17_long<- pivot_longer(dosage.chr17, cols = 4:ncol(dosage.chr17), names_to = "Ind", values_to = "allele_dosage") %>% 
  dplyr::select(-V3) 

dosage.chr17_long = left_join(dosage.chr17_long, Ind.id, by = "Ind")

write_tsv(dosage.chr17_long, "~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr17.VNqtl.beagle_alleledosage.txt")
```

## Plot genotype heatmaps

```{r}
dosage.chr17_long <- read_tsv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr17.VNqtl.beagle_alleledosage.txt")

dosage.chr17_long$Pop <- ordered(dosage.chr17_long$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))

dosage.chr17_long_plot <- dosage.chr17_long %>% 
  mutate(allele_dosage_rounded = as.character(round(allele_dosage))) %>% 
  ggplot(aes(x=as_factor(pos), y=Ind, fill = allele_dosage_rounded)) +
  geom_tile() +
  scale_fill_viridis_d(direction = 1) +
  facet_grid(Pop~chr, scales = "free", space = "free") +
  theme_bw() +
  theme(axis.text = element_blank(),
        axis.title = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        panel.margin.x = unit(0.2, "lines"),
        strip.text.y = element_text(angle = 0))
dosage.chr17_long_plot
```


```{r}
## define populations based on genotype and join with sample table
genotype_assn.chr17 <- dosage.chr17_long %>% 
  group_by(Ind) %>% 
  summarise(avg_dosage = mean(allele_dosage, na.rm = T))

genotype_assn.chr17.id <- Ind.id %>% left_join(genotype_assn.chr17, by = "Ind")
write_tsv(genotype_assn.chr17.id, "~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/beagle_files/mme_all_filtsnps_beagleGL_Mme_chr17.VNqtl.beagle_alleledosage_avg_byind.txt")
```

Correlation between chr17 allel dosage and VN number
```{r}
size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_data.csv", col_types = "ccdd")

chr17.size.alleledosage.df = inner_join(genotype_assn.chr17.id, size.df, by=c("Ind","Pop"))

chr17.size.alleledosage.df$Pop <- ordered(chr17.size.alleledosage.df$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))

chr17.size.alleledosage.plot = ggplot(data = chr17.size.alleledosage.df, aes(x=Pop, y=avg_dosage)) +
  geom_boxplot() +
  geom_hline(yintercept = mean(chr17.size.alleledosage.df$avg_dosage)) +
  ylim(c(0,2)) +
  scale_fill_manual(values = c("firebrick","steelblue")) +
  theme_cowplot() +
  ylab("Mean allele dosage") +
  xlab("Pop")

ggplot(data = chr17.size.alleledosage.df, aes(x=round(avg_dosage,digits = 0), y=StdLgth)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_cowplot() +
  ylab("length") +
  xlab("chr17")
```

Sum allele dosage
```{r}
## define populations based on genotype and join with sample table
genotype_assn.sum.chr17 <- dosage.chr17_long %>% 
  group_by(Ind) %>% 
  summarise(avg_dosage = sum(allele_dosage, na.rm = T))
genotype_assn.sum.chr17.id <- Ind.id %>% left_join(genotype_assn.sum.chr17, by = "Ind")

size.df = read_csv("~/Library/CloudStorage/Dropbox/Cornell_Postdoc/analysis/results/selection_analyses/inversion_bodysize_vn_associaton/silverside_bodysize_data.csv", col_types = "ccdd")

chr17.sum.size.alleledosage.df = inner_join(genotype_assn.sum.chr17.id, size.df, by=c("Ind","Pop"))

chr17.sum.size.alleledosage.df$Pop <- ordered(chr17.sum.size.alleledosage.df$Pop, levels = c("MAQU","HXNS", "MBNS", "MDME", "DXMA", "MCCT", "PANY", "CTVA", "OINC", "MCNC", "LRSC","JIGA"))
mme.pal <- c("#4f000b","#9e2a2b","#CE4257","darkorange2", "#ff9b54","#FFC100", "#edd746","#2a9d8f","#0f85a0","#05668D","#98C1d9", "#3d5a80") 

ggplot(data = chr17.sum.size.alleledosage.df, aes(y=round(avg_dosage,digits = 0), x=StdLgth)) +
  geom_point(shape=21, aes(fill=Pop)) +
  geom_smooth(method = "lm", color="grey10") +
  theme_cowplot() +
  scale_fill_manual(values = mme.pal) +
  ylab("sum(allele dosage) grQTL chr.17") +
  xlab("standard length (mm)")

chr17.sum.size.alleledosage.df.filt = na.omit(chr17.sum.size.alleledosage.df)
lmm.qtl17 <- lme(StdLgth ~ avg_dosage, random=~1 | Pop, data = chr17.sum.size.alleledosage.df.filt)
summary(lmm.qtl17)
anova(lmm.qtl17)

ggplot(data = chr17.sum.size.alleledosage.df, aes(y=round(avg_dosage,digits = 0), x=StdLgth)) +
  geom_point(shape=21, aes(fill=Pop)) +
  geom_smooth(method = "lm", aes(color=Pop)) +
  geom_smooth(method = "lm", color="grey40", linetype="dashed") +
  theme_cowplot() +
  ylab("sum(allele dosage) grQTL chr.17") +
  xlab("standard length (mm)")
```


```{r}
dosage.plots = (dosage_long_plot | chr13.vnqt.alleledosage.vn.plot) / (dosage.chr17_long_plot | chr17.size.alleledosage.plot)
```














